---
title: "Test Data Protocol 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(leaflet)
```

```{r}
Panoche <- read.csv("Panoche2.csv", header = TRUE)
Mojave <- read.csv("SampleDens.csv", header = TRUE)
Sites <- read.csv("PanocheSites.csv", header = TRUE)
```

###Summary Data of Mojave Sites
```{r}
summary(Mojave)
```
###Summary Data of Panoche Sites
```{r}
summary(Panoche)
```
###Summary Data of Panoche Site Locations
```{r}
summary(Sites)
```
###Sites Map in Panoche
```{r}
psites <- leaflet(Sites)%>%
  addTiles()%>%
  addCircles(lng = ~lng, lat = ~lat, weight = 1, radius = 20, popup = ~Site.Name)
psites
```

```{r}

```
###Visuals showing number of Shrubs per site in Panoche
```{r}
sitedensity <- Panoche$Site.ID
ggplot(data=Panoche, aes(Panoche$Site.ID)) +
  geom_histogram()
```
```{r}
ggplot(data = Panoche, aes(Site.ID, Shrub.ID)) +
  geom_point()
```
```{r}
ggplot(data = Panoche, aes(sitedensity, Site.ID)) +
  geom_boxplot()
```

###Correlation of site to X, Y, and Z measurements
```{r}
cor.test(Panoche$Site.ID, Panoche$x..m.)
cor.test(Panoche$Site.ID, Panoche$y..m.)
cor.test(Panoche$Site.ID, Panoche$z..m.)
```

```{r}
Panochelm <- lm(Site.ID ~ Shrub.ID, data = Panoche)
anova(Panochelm)
```

###Variance of Shrub Site, x, y, and z measurments
```{r}
var(Panoche$Site.ID)
var(Panoche$x..m.)
var(Panoche$y..m.)
var(Panoche$z..m.)
```

###Standard Error for Panoche Data
```{r}
sd(Panoche$Site.ID)
sd(Panoche$x..m.)
sd(Panoche$y..m.)
sd(Panoche$z..m.)
```

###T-test for panoche site
```{r}
t.test(Panoche$Site.ID)
```

###Data For Mojave
####Variance Data of X, Y, and Z
```{r}
var(Mojave$x..m.)
var(Mojave$y..m.)
var(Mojave$z..m.)
```

####Standard Error for X, Y, and Z in Mojave
```{r}
sd(Mojave$x..m.)
sd(Mojave$y..m.)
sd(Mojave$z..m.)
```

